test-mcda

### 2024-05-22 code/MCDA-EVSE.Rmd
testing the promethee method

performanceTable <- fishnet_nowater %>% dplyr::select(-c(uniqueID)) %>% st_drop_geometry()
uniqueIDs <- fishnet_nowater$uniqueID
rownames(performanceTable) <- uniqueIDs

```{r}
# reverse is min
weights <- c(0.2, 0.15, 0.1, 0.15, 0.2, 0.1, 0.05, 0.05)
criteriaMinMax <- c("min", "max", "max", "min", "max", "min", "min", "max")
overall1 <- TOPSIS(performanceTable, weights, criteriaMinMax)
TOPSIS <- data.frame(uniqueID = names(overall1), values = overall1) %>%  
  mutate(uniqueID = as.integer(uniqueID)) %>%

@@

>>>>

performanceTable <- fishnet_nowater %>% 
  dplyr::select(-c(uniqueID)) %>% 
  st_drop_geometry() %>% 
  mutate(density = scale_values(density),
         TSFCA = scale_values(TSFCA),
         driving_pop = scale_values(driving_pop),
         evse.nn = scale_values(evse.nn),
         elec_cnt = scale_values(elec_cnt),
         parking.nn = scale_values(parking.nn),
         policefire.nn = scale_values(policefire.nn)
         )
uniqueIDs <- fishnet_nowater$uniqueID
rownames(performanceTable) <- uniqueIDs
```

```{r}
overall1
```

```{r}
# reverse is min
weights <- c(0.2, 0.15, 0.1, 0.15, 0.2, 0.1, 0.05, 0.05)
criteriaMinMax <- c("min", "max", "max", "min", "max", "min", "min", "max")
overall1 <- TOPSIS(performanceTable, weights, criteriaMinMax)
TOPSIS <- data.frame(uniqueID = names(overall1), values = overall1) %>%  
  mutate(uniqueID = as.integer(uniqueID))

@@

## Self Assigned Weights + PROMETHEE

The function returns three matrices: The first one contains the preference relations between the
alternatives, the second one contains the indifference relations between the alternatives and the
third one contains the incomparability relations between the alternatives.

# performance table: matrix where each row corresponds to an alternative,and each column to a criterion
# preference function
# preference threshold
# indifference threshold
# gauss parameter
# criteria weights
# criteria minmax

### 2024-05-22 code/test-mcda.Rmd
testing the promethee method

>>>>

## Testing the PROMETHEE Approach

The function returns three matrices: The first one contains the preference relations between the
alternatives, the second one contains the indifference relations between the alternatives and the
third one contains the incomparability relations between the alternatives.

performanceTable <- rbind(
c(1,10,1),
c(4,20,2),
c(2,20,0),
c(6,40,0),
c(30,30,3))
rownames(performanceTable) <- c("RER","METRO1","METRO2","BUS","TAXI")
colnames(performanceTable) <- c("Price","Time","Comfort")
```

```{r}
# The preference functions
preferenceFunction<-c("Gaussian","Level","V-shape-Indiff")
```

```{r}
#Preference threshold
preferenceThreshold<-c(5,15,3)
names(preferenceThreshold)<-colnames(performanceTable)
```

```{r}
#Indifference threshold
indifferenceThreshold<-c(3,11,1)
names(indifferenceThreshold)<-colnames(performanceTable)

#Parameter of the Gaussian preference function
gaussParameter<-c(4,0,0)
names(gaussParameter)<-colnames(performanceTable)

#weights
criteriaWeights<-c(0.2,0.3,0.5)
names(criteriaWeights)<-colnames(performanceTable)

# criteria to minimize or maximize
criteriaMinMax<-c("min","min","max")
names(criteriaMinMax)<-colnames(performanceTable)

PROMETHEEOutrankingFlows(performanceTable, preferenceFunction,preferenceThreshold,
indifferenceThreshold,gaussParameter,criteriaWeights,criteriaMinMax)
```
